\documentclass[12pt, reqno]{amsart}

\textwidth=7in
\textheight=9.5in
\topmargin=0in
\headheight=0in
\headsep=.5in
\hoffset=-.85in

\begin{document}

\title[Math 250 Handout 1 - Logic]{Math 250 Handout 1 - Logic}\maketitle


A \textbf{statement} is a sentence for which `true or false' is meaningful.
\\

1. Which of these are \textbf{statements}? 
\vspace{10pt}
\begin{enumerate}
\item Today it is raining.
\item What is your name?
\item Every student in this class is a math major.
\item $2 + 2 = 5$.
\item $x + 1  > 0$.
\item $x^2 + 1  > 0$.
\item If it is raining, then I will wear my raincoat.
\item Give me that.
\item This sentence is false.
\item If $x$ is a real number, then $x^2 > 0$.
\end{enumerate}
\vspace{20pt}

2. Which of these are true? 
\vspace{10pt}
\begin{enumerate}
\item (T or F) Every student in this class is a math major and a human being.
\item (T or F) Every student in this class is a math major or a human being.
\item (T or F) $2 + 2 = 5$ or  $1  > 0$.
\item (T or F) If $x$ is a real number, then $x^2 \geq 0$.
\item (T or F) If $x$ is a complex number, then $x^2 \geq 0$.
\end{enumerate}
\vspace{20pt}

3. Write the negations of the following.
\vspace{10pt}
\begin{enumerate}
\item $2 + 2 = 5$
\item $1  > 0$.
\item $2 + 2 = 5$ or  $1  > 0$.
\item Every student in this class is a math major.
\item Every student in this class is a math major or a human being.
\item If $x$ is a real number, then $x^2 > 0$.
\end{enumerate}
\vspace{20pt}

4. Prove the following using truth tables.
\vspace{10pt}
\begin{enumerate}
\item $P \wedge(  Q\vee R) = (P\wedge Q) \vee (P \wedge R)$,
\item $(P \vee Q) \vee R = P \vee (Q \vee R)$. (We thus write $P \vee Q \vee R$ for both.)
\item \label{enum:distNeg} $\neg (P \vee Q) = \neg P \wedge \neg Q$,
\item $\neg (P \wedge Q) =$ (make a guess similar to problem \ref{enum:distNeg}),
\item $\neg (\neg P) = P$.
\end{enumerate}
\vspace{20pt}

\newpage

5. In exercise 6, you may use the following variants of exercise 4.
\vspace{10pt}
\begin{enumerate}
\item $P \vee(  Q\wedge R) = (P\vee Q) \wedge (P \vee R)$,
\item $(P \wedge Q) \wedge R = P \wedge (Q \wedge R)$. (We thus write $P \wedge Q \wedge R$ for both.)
\item $P \vee Q = Q \vee P$.
\item $P \wedge Q = Q \wedge P$.
\end{enumerate}
\vspace{20pt}

6. Prove or disprove the following \emph{without} using truth tables. 
\vspace{10pt}
\begin{enumerate}
\item $\neg(P \wedge \neg Q) = \neg P \vee Q$.
\item $P \vee ((Q \wedge R) \wedge S) = (P \wedge Q) \vee (P \wedge R)
  \vee (P \wedge S)$.
\item $P \vee (Q \wedge R) \wedge S) = (P \vee Q) \wedge (P \vee R)
  \wedge (P \vee S)$.

\end{enumerate}
\vspace{20pt}

7. Write the negations of the following implications.
\vspace{10pt}
\begin{enumerate}
\item If $n$ is even, then $n^2$ is even.
\item If $1 = 0$, then $2 + 2 = 5$.
\item If there is free coffee, then DZB will drink it
\item If $1 = 0$ and $2 + 2 = 5$, then the sky is blue and kittens are popular on youtube
\item If $x$ and $y$ are real numbers such that $xy = 0$, then $x = 0$ or $y = 0$.
\end{enumerate}
\vspace{20pt}

8. Which of these are true? 
\vspace{10pt}
\begin{enumerate}
\item (T or F) For all $x \in \mathbf{Z}$, $x$ is divisible by 2.
\item (T or F) There exists an $x \in \mathbf{Z}$ such that $x$ is divisible by $2$.
\item (T or F) For all $x \in \mathbf{R}$, if $x \neq 0$, then there exists a $y \in \mathbf{R}$ such that $xy = 1$.
\item (T or F) For all $x \in \mathbf{R}$, there exists a $y \in \mathbf{R}$ such that $xy = 1$.
\end{enumerate}
\vspace{20pt}

9. Write the negations of the following.
\vspace{10pt}
\begin{enumerate}
\item For all $x \in \mathbf{Z}$, $x$ is divisible by 2.
\item There exists an $x \in \mathbf{Z}$ such that $x$ is divisible by $2$.
\item $\neg(\forall x, P(x))$,
\item $\neg( \exists x $ s.t. $Q(x)$)
\item $\forall x, (P(x) \wedge Q(x))$.
\item If $\exists x \in \mathbf{R}$ such that $2x = 1$, then for all $y$, $y^2 < 0$.  
\item For all $x \in \mathbf{R}$, there exists a $y \in \mathbf{R}$ such that $xy = 1$.
\end{enumerate}
\vspace{20pt}

10. Write the converse and contrapositive of the statements from problem 7.


\newpage


Here are some basic identities.
\begin{enumerate}
\item $P \wedge Q = Q \wedge P$
\item $P \vee Q = Q \vee P$
\item $(P \wedge Q) \wedge R = P \wedge (Q \wedge R) = P \wedge Q \wedge R$
\item $(P \vee Q) \vee R = P \vee (Q \vee R) = P \vee Q \vee R$  
\end{enumerate}
\smallskip

Here are some useful identities.

\begin{enumerate}
\item $\neg(P \wedge Q) = \neg P \vee \neg Q$
\item $\neg(P \vee Q) = \neg P \wedge \neg Q$
\item $\neg(\neg P) = P$
\item $P \vee (Q \wedge R) = (P \vee Q) \wedge (P \vee R)$
\item $P \wedge (Q \vee R) = (P \wedge Q) \vee (P \wedge R)$
\item $\neg (P \Rightarrow Q) = P \wedge \neg Q$
\item $\neg (\forall x, P(x)) = \exists x$  such that $\neg P(x)$
\item $\neg (\exists x$ such that $P(x)) = \forall x, \neg P(x)$

\end{enumerate}
\vspace{10pt}

We can combine these to negate more complicated statements

\begin{enumerate}
\item $\neg(P \Rightarrow (Q \vee R)) = $ 
\item [] $P \wedge \neg (Q \vee R)) = $ 
\item [] $P \wedge \neg Q \wedge \neg R$ 
\item []
\item If $1 = 0$ and $2 + 2 = 5$, then the sky is blue and kittens are cute
\item [] If (P and Q) then (R and T)
\item [] 
\item [] Its negation:
\item [] (P and Q) and not (R and T)
\item [] ($1 = 0$ and $2 + 2  = 5$) and (the sky is not blue or kittens are not cute)
\item []
\item $\neg Q \Rightarrow \neg P$
\item [] $\neg (\neg Q \Rightarrow \neg P)$
\item [] $\neg Q \wedge \neg(\neg P)$
\item [] $\neg Q \wedge P$
\end{enumerate}

\vspace{10pt}

This last example is called the \textbf{contrapositive}, and is a useful proof technique! (Try it on your homework.)
\\

\begin{enumerate}
\item[] $(P \Rightarrow Q) = (\neg Q \Rightarrow \neg P)$ because they have the same negation.
\end{enumerate}






\end{document}

