\documentclass[12pt]{article}

% Easy way to fix the margins with a package
\textwidth=7in
\textheight=9.5in
\topmargin=-1in
\headheight=0in
\headsep=.5in
\hoffset -.85in

\setcounter{secnumdepth}{0}

\usepackage{hyperref}
\hypersetup{
 colorlinks=true,
 linkcolor=blue,
 filecolor=magenta,
 urlcolor=cyan,
}

\usepackage{amssymb, latexsym, amsmath, verbatim, multicol}
\newcommand{\N}{{\mathbb N}}
\newcommand{\Z}{{\mathbb Z}}
\newcommand{\C}{{\mathbb C}}
\newcommand{\R}{{\mathbb R}}
\newcommand{\Q}{{\mathbb Q}}

\pagestyle{empty}

\begin{document}
\noindent\rule{18cm}{0.4pt}
\begin{center}
 {\bf MATH 250, Foundations of Mathematics (IN PROGRESS)
}

{\bf
 % Section 001 Wed 11:20 - 12:35 
 Section 003 TuTh 2:30 - 3:45
}
 \end{center}
\noindent\rule{18cm}{0.4pt}

% \renewcommand{\arraystretch}{2}

\vskip.25in
\begin{center}
 \noindent\textbf{All assignments}\\
 Last updated: \today
\end{center}
\noindent\rule{18cm}{0.4pt}
\tableofcontents

\newpage
\section[1 (due January 18): Introduction to course. Mathematical reasoning.]{Assignment 1}

\textbf{Topics}: Introduction to the course. Mathematical reasoning.
\\

\noindent \textbf{Reading}: Chapter 1, except for proof by contradiction.
\\

\noindent \textbf{Suggested problems (do not hand in)}

\begin{itemize}
\item With answers:
 \begin{itemize}
 \item Section 1.1, \#1(adgj), 2(adji), 3(adgi), 5(ad), 6(a)
 \item Section 1.2, \#2(ac), 4(ac), 5(ad), 7(a), 10(a), 11(a), 12(a)
 \item Section 1.3, \#1(ad), 3(a), 5(ac), 7(ac)
 \item Section 1.4, \#1, 4(a), 6(a), 8, 12(ab), 15(a)

\end{itemize}

\item Without answers: \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H01-logic.pdf}{Handout 1}

\end{itemize}

\noindent \textbf{Assignment, due Tuesday, January 18, via Canvas}:
\begin{enumerate}
\item Suppose that $n$ is an even integer, and let $m$ be any integer. Prove that $nm$ is even. 
\item Suppose that $n$ is an odd integer. Prove that $n^2$ is an odd integer. (Hint: an integer $n$ is odd if and only if there exists an integer $k$ such that $n = 2k+1$.)
\item Prove that if $n^2$ is even, then $n$ is even. (Hint: see Section 1.4)
\item Write the negation of each of the following statements.

 \begin{enumerate}
\item All triangles are isosceles.
\item Every door in the building was locked.
\item Some even numbers are multiples of three.
\item Every real number is less than 100.
\item Every integer is positive or negative.
\item If $f$ is a polynomial function, then $f$ is continuous at $0$.
\item If $x^2 > 0$, then $x > 0$.
\item There exists a $y \in \mathbf{R}$ such that $xy = 1$.
\item $(2 > 1)$ and $(\forall x, x^2 > 0)$
\item $\forall \epsilon > 0$, $\exists \delta > 0$ such that if $|x| < \delta$, then $|f(x)| < \epsilon$.
\end{enumerate}
\end{enumerate}

\newpage
\section[2 (due January 25): Divisibility problems.]{Assignment 2}

\textbf{Topics}: ``Basic'' proofs and divisibility problems. 
\\



\noindent \textbf{Reading}:
\begin{itemize}
\item Finish reading chapter 1.
\item Section 5.3
\end{itemize}



\noindent \textbf{Suggested problems (do not hand in)}

\begin{enumerate}
\item With answers: Section 5.3, \#1(a), 4(a), 6(ac)

\item Without answers: Section 5.3, \#2, 4 (without induction), 5 (without induction)

\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H02-divisibility.pdf}{Handout 2}
\end{enumerate}


\noindent \textbf{Assignment, due Tuesday, January 25, via Canvas}:

\begin{enumerate}
\item Prove that if $x$ is an integer, then $x^2 + 2$ is not divisible by 4. (Hint: there are two cases: $x$ is even, $x$ is odd. Also, feel free to use basic facts about even or odd, e.g., ``odd + odd = even'', without additional proof.)
\item Prove that the product of three consecutive integers is divisible by 6. (It suffices to prove that it is divisible by 2 and 3 separately.)
\item Show that for all integers $a$ and $b$, 
\[
a^2b^2(a^2 - b^2)
\]
is divisible by 12. (It suffices to prove that it is divisible by 4 and 3 separately.)
\item Find all positive integers $n$ such that $n^2 - 1$ is prime. Prove that your answer is correct.

\end{enumerate}


\newpage
\section[3 (due February 8): Proof by contradiction. Unsolvability. Irrationality.]{Assignment 3}

\textbf{Topics}: Proof by contradiction. Unsolvability of equations. Irrationality.
\\

\noindent \textbf{Reading}:
\begin{itemize}
\item Section 1.4, p.~41-42 (stop at Historical Comments)
\item Section 5.4
\end{itemize}




\noindent \textbf{Suggested problems (do not hand in)}

\begin{enumerate}
\item Without answers: Section 1.4 \#21
\item Without answers: Section 5.4 \#6, 7, 10(a), 15, 18,
\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H03-contradiction.pdf}{Handout 3}
\end{enumerate}


\noindent \textbf{Assignment, due Tuesday, February 8, via Canvas}:
\begin{enumerate}
% \item Prove that the equation $x^2 = 4y + 3$ has no integer solutions. (Hint: there are two cases. Either $x$ is even, or $x$ is odd. Consider each case separately and try to get a contradiction.)
 % \item Section 5.4, \#13, \#14.
\item Prove that $2^{1/3}$ is irrational.
\item Prove that there are no positive integer solutions to the equation $x^2 - y^2 = 10$.
\item Let $a, b, c$ be integers satisfying $a^2 + b^2 = c^2$. Show that $abc$ must be even. (Harder problem, just for fun: show that $a$ or $b$ must be even.)
\item Suppose that $a$ and $n$ are integers that are both at least 2. Prove that if $a^n -1$ is prime, then $a = 2$ and $n$ is a prime. (Primes of the form $2^n - 1$ are called Mersenne primes.)
\end{enumerate}



\newpage
\section[4 (due February 15): Induction.]{Assignment 4}

\textbf{Topics}: Induction.
\\

\noindent \textbf{Reading}: Section 5.2, p.~159-163
\\

\noindent \textbf{Fun Video}: Vi Hart; ``Doodling in Math: Spirals, Fibonacci, and Being a Plant''

\noindent \url{https://www.youtube.com/watch?v=ahXIMUkSXX0}
\\ 

\noindent \textbf{Suggested problems (do not hand in)}

\begin{enumerate}
\item With answers: Section 5.2 \#1(a), 4(a), 8(ad), 9(a), 29
\item Without answers: Section 5.2 \#2-9, 13
\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H04-induction-warmup.pdf}{Handout 4}
\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H05-induction-problems.pdf}{Handout 5}
\end{enumerate}

\noindent \textbf{Assignment, due Tuesday, February 15, via Canvas}:
\begin{enumerate}
% \item Prove that for every positive integer $n$,
% $$1^2 + 2^2 + \ldots n^2 = \frac{n(n+1)(2n+1)}{6}.$$
\item Prove that for every positive integer $n$,
 $$1^3 + 2^3 + \cdots +n^3 = \frac{n^2(n+1)^2}{4}.$$ 
\item Let $a_n$ be defined recursively by $a_1 = 1$ and $a_n = \sqrt{1 + a_{n-1}}$. Prove that for all positive integers $n$, $a_n < 2$.
\item Prove by induction that if $b_1, b_2, \ldots , b_n$ are even integers, then $b_1 + b_2 + \cdots + b_n$ is even.
 \item Let $F_1, F_2, F_3, \ldots = 1,1,2,3,5,8,\ldots$ be the Fibonacci sequence. Prove that $F_1^2 + \cdots + F_n^2 = F_nF_{n+1}$.
 \end{enumerate}
 

\newpage
\section[5 (due February 22): Basics of set theory. Basic operations. Proofs with sets.]{Assignment 5}

\textbf{Topics}: Basics of set theory. Basic operations. Proofs with sets.
\\

\noindent \textbf{Reading}:
\begin{enumerate}
\item Section 2.1, p.~49-57; 
\item Section 2.2, p.~61-65 (stop at DeMorgan's laws)
\end{enumerate}




\noindent \textbf{Suggested problems (do not hand in)}

% Section 2.1, \#7,9,12,14,21,D1 \#13, \#18a, 19a-c, 20e-f, ยง2.2, \#14, \#26 (2.1) 6,7,9,10,12,13

\begin{enumerate}
\item With answers (many of these are calculations; do as many as you need to do to understand the definitions):
 \begin{enumerate}
 \item Section 2.1, \#1(adg), 2(adg), 4(adg), 5(a), 7(a), 8(ae), 9(adf), 10(a), 18(acf), 19(ad), 20(ae), 21
 \item Section 2.2, \#1(adgj), 2(ad), 4(ad), 5(ad), 7(a), 9(ad), 14(a),
\end{enumerate}

\item Without answers:
 \begin{enumerate}
 \item Section 2.1, 13, 14, 15, 16, 
 \item Section 2.2, \#1-12
 \end{enumerate}

\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H06-sets-I.pdf}{Handout 6}
\end{enumerate}

\noindent \textbf{Assignment, due Tuesday, February 22, via Canvas}:
\begin{enumerate}
\item Let $A = \{ n \in \Z | n \text{ is a multiple of } 4\}$ and $B = \{ n \in \Z | n^2 \text{ is a multiple of } 4\}$ 
 \begin{enumerate}
 \item Prove or disprove: $A \subset B$. 
 \item Prove or disprove: $B \subset A$. 
 \end{enumerate}

\item Prove that $A \cup (A \cap B) = A.$
\item Let $A,B$ and $C$ be sets. 
 \begin{enumerate}
 \item Prove that $(A \subset C) \wedge (B \subset C) \Rightarrow A \cup B \subset C$.
 \item State the contrapositive of part (a).
 \item State the converse of part (a). Prove or disprove it.
 \end{enumerate}
% \item Let $A = \{ n \in \Z | n = 8t+7 \text{ for some } t \in \Z \}$ and $B = \{ n \in \Z | n = 4t + 3 \text{ for some } t \in \Z\}$ 
% \begin{enumerate}
% \item Prove of disprove: $A \subset B$. 
% \item Prove of disprove: $B \subset A$. 
% \end{enumerate}
\item Let $n$ and $m$ be integers. Prove that if $n\Z \subset m\Z$ then $m$ divides $n$.
\end{enumerate}


% Shpeal about sets (containers, some examples, anything can be a set).
% How to do proofs with sets. Subset. Definition is an implication. What is your hypothesis? Conclusion? One example, then transitivity. 
% Empty set. Set containing empty set. Worksheet?

\newpage
\section[6 (due March 1): More sets. DeMorgan's laws. Cartesian Products. Power sets.]{Assignment 6}

\textbf{Topics}: More proofs with sets. DeMorgan's laws. Cartesian Products. Power sets
\\

\noindent \textbf{Reading}:
\begin{enumerate}
\item Section 2.2, p.~65-66; 
\item Section 2.3, p.~72, just the part about
 power sets.
\end{enumerate}


% 2 minutes about DeMorgan's laws. https://www.youtube.com/watch?v=-LW2lGHv0GE 



\noindent \textbf{Suggested problems (do not hand in)}
 
\begin{enumerate}
\item With answers:
 \begin{enumerate}
 \item Section 2.2, 13(a), 16(a) 
 \item Section 2.3, \#1(a), 3, 5(adg),
 \end{enumerate}

\item Without answers:
 \begin{enumerate}
 \item Section 2.2, 14, 16-19, 21, 23-27
 \item Section 2.3, \#1(b), 2,4
 \end{enumerate}

 \item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H07-sets-II.pdf}{Handout 7}
\end{enumerate}


\noindent \textbf{Assignment, due Tuesday, March 1, via Canvas}:

\begin{enumerate}
\item Let $A$ and $B$ be sets. Prove that $(A \cup B) \cap \overline{A} = B - A$.
\item Let $A$ and $B$ be sets. Prove that $(A \cup B) - (A \cap B) = (A - B) \cup (B - A)$.
\item Let $A = \{0,1,2\}$. Which of the following statements are true? (No justification is needed.)

 \begin{enumerate}
 \item $\{0\} \subset P(A)$;\vspace{0.3cm}
 \item $\{1,2\} \in P(A)$;\vspace{0.3cm}
 \item $\{1,\{1\}\} \subset P(A)$.\\ 
 \item $\{\{0,1\},\{1\}\} \subset P(A)$;\vspace{0.3cm}
 \item $\emptyset \in P(A)$;\vspace{0.3cm}
 \item $\emptyset \subset P(A)$;\vspace{0.3cm}
 \item $\{\emptyset\} \in P(A)$. \vspace{0.3cm}
 \item $\{\emptyset\} \subset P(A)$;\vspace{0.3cm}

 \end{enumerate}
\item Let $A$ and $B$ be sets. Prove that if $A \subset B$, then $P(A) \subset P(B)$. State the converse of this and prove or disprove it.

\end{enumerate}


\newpage
\section[ (March 3) Midterm ]{Midterm}

\textbf{Topics}: Tuesday, March 1 will be Exam review. We will not cover any new material; in class, I will answer whatever questions you have. The exam is on Thursday, March 3.
\textbf{Please show up with questions}.
\\

\noindent \textbf{Content}: The questions will all be either
\begin{enumerate}
\item homework problems,
\item suggested problems,
\item problems we worked in class, or
\item minor variations of one of these.
\end{enumerate}


% \noindent \textbf{Fall Break is Monday, 11 and Tuesday, 12; no class or office hours these days}.
% \\



%% \noindent I will hold \textbf{office hours} on \textbf{Wednesday, 18} at 5:30-6:30.

\newpage
\section[7 (due March 22): Introduction to functions; images and surjectivity.]{Assignment 7}

\textbf{NO CLASS March 8, 10; spring break}

\textbf{Topics}: Introduction to functions; images and surjectivity
\\

\noindent \textbf{Reading}:
\begin{enumerate}
\item Section 3.1, p.~81-90 (stop at ``Inverse Image'');
\item Section 3.2, p.~97-100 (stop at Injective Functions).
\end{enumerate}




\noindent \textbf{Suggested problems (do not hand in)}

\begin{enumerate}
\item With answers:
  \begin{enumerate}
\item Section 3.1, \#1(adg), 4(ace), 5(a), 8(a), 10(a), 12(1d)
\item Section 3.2, \#1(adgj), 2(ad)
\end{enumerate}  
\item Without answers:
  \begin{enumerate}
\item Section 3.1, 1-4,6-13
\item Section 3.2, 1-6
\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H09-images.pdf}{Handout 9}
  \end{enumerate}    
\end{enumerate}


\noindent \textbf{Assignment, due Tuesday, March 22, via Canvas}:
\begin{enumerate}

\item Let $f \colon \mathbf{R} \to \mathbf{R}$ be the function defined by $f(x) = 6x+5$.
 \begin{enumerate}
 \item Prove that $f(\mathbf{R}) = \mathbf{R}$.
 \item Compute $f([1,4])$. Prove your answer.
 \end{enumerate}
\item Let $f \colon \mathbf{R} \to \mathbf{R}$ be the function defined by $x^4 + x^2$. 
 \begin{enumerate}
 \item Compute the image of $f$. Prove that your answer is correct.
 \item Compute $f([-1,2])$. Prove that your answer is correct.
\end{enumerate}

\item Let $A$ and $B$ be sets and let $X$ and $Y$ be subsets of $A$. Let $f\colon A \to B$ be a function. Prove or disprove each of the following. When giving a disproof, please give an counterexample.
 \begin{enumerate}

  \item $f(X \cap Y) \subset f(X) \cap f(Y)$.
  \item $f(X \cap Y) \supset f(X) \cap f(Y)$.
  \item $f(X) - f(Y) \subset f(X - Y)$.
  \item $f(X) - f(Y) \supset f(X - Y)$.

 \end{enumerate}

 

\end{enumerate}


\newpage
\section[8 (due March 29): Inverse Image (or ``Preimage'').]{Assignment 8}

\textbf{Topics}: Inverse Image (or ``Preimage'').
\\

\noindent \textbf{Reading}: Section 3.1, p.~90-92 (stop at the Historical Comments. Or don't.)
\\



\noindent \textbf{Suggested problems (do not hand in)}

\begin{enumerate}
\item With answers: Section 3.1, \#17(ad), \#18(adg), \#19(a), \#21(a)
\item Without answers: 17-21
\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H10-preimages.pdf}{Handout 10}
\end{enumerate}


\noindent \textbf{Assignment, due Tuesday, March 29, via Canvas}:
\begin{enumerate}
\item Let $f \colon \mathbf{R} \to \mathbf{R}$ be the function defined by $f(x) = 3x+1$. 
 \begin{enumerate}
 \item Compute $f^{-1}(\{1,5,8\})$ (do not give a proof).
 \item Compute $f^{-1}(W)$, where $W = (4,\infty)$, and give a proof that your answer is correct.
 \item Compute $f^{-1}(\mathbf{E})$, where $\mathbf{E}$ is the set of even integers, and give a proof that your answer is correct.
 \end{enumerate}

\item Let $f \colon \mathbf{Z} \to \mathbf{Z}$ be the function defined by $f(n) =
 \begin{cases}
 \frac{n}{2}, & \text{if $n$ is even} \\
 2n+4, & \text{if $n$ is odd}.
 \end{cases}
 $
 
 Compute $f^{-1}(\mathbf{E})$. Prove that your answer is correct. (Reminder: $\mathbf{E}$ is the set of even integers.)
\item Let $A$ and $B$ be sets and let $X$ be a subset of $B$. Let $f\colon A \to B$ be a function. Prove or disprove the following. (For a disproof, please give an explicit counterexample.)
 \begin{enumerate}
 \item $X \subset f(f^{-1}(X))$.
 \item $X \supset f(f^{-1}(X))$.
 \end{enumerate}

\item Let $A$ and $B$ be sets. Let $S \subset A$ and let $T \subset B$. Let $f\colon A \to B$ be a function. Prove or disprove the following. (For a disproof, please give an explicit counterexample.)
 \begin{enumerate}
 \item $f(S) \subset T \Rightarrow S \subset f^{-1}(T)$.
 \item $S \subset f^{-1}(T) \Rightarrow f(S) \subset T$.
 \end{enumerate}
 
\end{enumerate}


\newpage
\section[9 (due April 5): Injectivity.]{Assignment 9}

\textbf{Topics}: Injectivity.
\\

\noindent \textbf{Reading}: Section 3.2, p.~100-105
\\





\noindent \textbf{Suggested problems (do not hand in)}

\begin{enumerate}
\item With answers: 3.2, \#12(adg), \#13(bd)
\item Without answers: 3.2 \#9-14, 19(abc)
\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H11-injectivity.pdf}{Handout 11}
\end{enumerate}


\noindent \textbf{Assignment, due Tuesday, April 5, via Canvas}:
\begin{enumerate}
\item Which of the following functions $f \colon \mathbf{R}\to \mathbf{R}$ are injective? If the function is injective, give a proof. If it is not injective, give a counterexample.
 \begin{enumerate}
 \item $f(x) = x^4 + x^2$;
 \item $f(x) = x^3 + x^2$;
 \item $f(x) =
 \begin{cases}
 -x-1, & \text{if $x > 0$} \\
 x^2, & \text{if $x \leq 0$}.
 \end{cases}
 $ 
 \end{enumerate}
\item Let $A$ and $B$ be sets and let $X$ and $Y$ be subsets of $A$. Let $f \colon A \to B$ be an injective function. Prove that $f(X \cap Y) = f(X) \cap f(Y)$.
\item Let $f \colon A \to B$ be a function. Which of the followings statements are equivalent to the statement `$f$ is injective'? (No proof necessary.)
 \begin{enumerate}
 \item $f(a) = f(b)$ if $a = b$;
 \item $f(a) = f(b)$ and $a = b$ for all $a,b \in A$;
 \item If $a$ and $b$ are in $A$ and $f(a) = f(b)$, then $a = b$;
 \item If $a$ and $b$ are in $A$ and $a = b$, then $f(a) = f(b)$;
 \item If $a$ and $b$ are in $A$ and $f(a) \neq f(b)$, then $a \neq b$;
 \item If $a$ and $b$ are in $A$ and $a \neq b$, then $f(a) \neq f(b)$. 
 \end{enumerate}
\item We define a function $f\colon [a,b] \to \mathbf{R}$ to be \textbf{decreasing} if for all $x_1,x_2 \in [a,b]$, if $x_1 < x_2$, then $f(x_1) > f(x_2)$.
 \begin{enumerate}
 \item Negate the definition of decreasing.
 \item Prove that a decreasing function is injective.
 \end{enumerate}
\end{enumerate}


\newpage
\section[10 (due April 12): Composition of functions.]{Assignment 10}

\textbf{Topics}: Composition of functions.
\\

\noindent \textbf{Reading}: Section 3.3, p.~110-113
\\


\noindent \textbf{Suggested problems (do not hand in)}

\begin{enumerate}
\item With answers: 3.3, \#1(a), 2(a), 3(ad), 7(a)
\item Without answers: 3.3 \#1-7, 9
\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H12-compositions.pdf}{Handout 12}
\end{enumerate}


\noindent \textbf{Assignment, due Tuesday, April 12, via Canvas}:
\begin{enumerate}
\item Let $A, B$ and $C$ be sets and let $f \colon A \to B$ and $g \colon B \to C$ be functions. Prove or disprove each of the following.
 \begin{enumerate}
 \item If $g\circ f$ is an injection, then $g$ is an injection.
 \item If $g\circ f$ is a surjection, then $f$ is a surjection.
 \item If $g\circ f$ is a surjection, then $g$ is a surjection.
 \end{enumerate}
\item Let $A$ and $B$ be sets and let $f \colon A \to B$ and $g \colon B \to A$ be functions. Prove that if $g \circ f$ and $f \circ g$ are bijective, then so are $f$ and $g$.
\item Let $f\colon A \to B$ be a function. Let $X,Y \subset A$. The following statement is false as stated
 $$f(X \cap Y) \supset f(X) \cap f(Y).$$
Does the statement become true if we add the hypothesis that $f$ is injective? Surjective? In each case, prove your assertion or give a counterexample. \textbf{Replace this with another problem}
 \\
 \item Let $f \colon \R \to \R$ and $g \colon \R \to \R$ be functions. Suppose that $f$ and $g$ are both decreasing. Prove that $g \circ f$ is decreasing.
 \end{enumerate}
 
\newpage
\section[11 (due April 19): Inverse functions.]{Assignment 11}

\textbf{Topics}: Inverse functions.
\\

\noindent \textbf{Reading}: Section 3.3, p.~114-116
\\

\noindent \textbf{Suggested problems (do not hand in)}

\begin{enumerate}
\item With answers: 3.3 \#10(adgj), 11(a)
\item Without answers: 3.3 \#10, 12, 14, 15, 17, 18, 19, 22
\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H13-inverses.pdf}{Handout 13}
\end{enumerate}


\noindent \textbf{Assignment, due Tuesday, April 19, via Canvas}:
\begin{enumerate}
\item Define $f \colon \mathbf{R}-\{1\} \to \mathbf{R} - \{1\}$ by $f(x) = \frac{x+1}{x-1}$. Prove that $f$ is a bijection. Find a formula for the inverse $f^{-1}(x)$, and prove that it is correct.
\item Let $A, B$ and $C$ be sets and let $f \colon A \to B$ and $g \colon B \to C$ be functions. Prove that if $f$ and $g$ are invertible, then so is $g \circ f$, and prove that $(g \circ f)^{-1} = f^{-1} \circ g^{-1}$.
\item Let $f \colon \mathbf{R} \to \mathbf{R}$ be the function $f(x) = x^3 + x$. Prove that $f$ is invertible without finding a formula for $f^{-1}$.
\item Let $A$ and $B$ be sets and let $f \colon A \to B$ be a function. Suppose that $f$ has a \emph{left inverse} $g$; that is, suppose that there exists a function $g \colon B \to A$ such that $g \circ f = id_A$. Prove that $f$ is injective.
\end{enumerate}


\newpage
\section[12 (due April 25): Relations]{Assignment 12}

\textbf{Topics}: Relations.
\\

\noindent \textbf{Reading}: Section 4.2, p.~139-144 (stop at the proof of Theorem 4.2.6)
\\



\noindent \textbf{Suggested problems (do not hand in)}

\begin{enumerate}
\item With answers: Section 4.2 \#1(a), 3(ad), 4(a), 5(a), 12(a)
\item Without answers: Section 4.2 \#1, 3, 4
\item \href{https://www.math.emory.edu/~dzb/teaching/250Fall2021/handouts/250-H14-equivalence-relations.pdf}{Handout 14}
\end{enumerate}


\noindent \textbf{Assignment, due Monday, April 25, 11:59PM, via canvas}:
\begin{enumerate}
\item Let $A = \{1,2,3\}$ and define a relation on $A$ by $a \sim b$ if $a + b \neq 3$. Determine whether this relation is reflexive, symmetric, transitive, or antisymmetric.
\item Define a relation on $\mathbf{Z}$ given by $a \sim b$ if $a-b$ is divisible by $4$.
 \begin{enumerate}
 \item Prove that this is an equivalence relation.
 \item What integers are in the equivalence class of 18? (No proof necessary.)
 \item What integers are in the equivalence class of 31? (No proof necessary.) 
 \item How many distinct equivalence classes are there? What are they? (No proof necessary.)
 \end{enumerate}
\item Define a relation on $\mathbf{Z}$ given by $a \sim b$ if $a^2-b^2$ is divisible by $4$.
 \begin{enumerate}
 \item Prove that this is an equivalence relation.
 \item How many distinct equivalence classes are there? What are they? (No proof necessary.)
 \end{enumerate} 
\item Let $A$ be a set, and let $P(A)$ be the power set of $A$. Assume that $A$ is not the empty set. Define a relation on $P(A)$ by $X \sim Y$ if $X \subset Y$. Is this relation reflexive, symmetric, and/or transitive? In each case give a proof, or disprove with a counterexample. (For a counterexample, give an example of $A$, $X$, and $Y$ that disproves the statement.)
\end{enumerate}


\noindent \textbf{Please note the unusual due date of the homework assignment}.


\newpage
\section[Final Exam]{Final Exam}

\textbf{Final exam} is Thursday May 3, 3:00pm - 5:30pm
\\

\noindent The \textbf{last day of class} is April 21. 
\\

\noindent There will be \textbf{office hours} on Wednesday, May 2, 4:30-6:30, via Zoom. 
\\


% \section[Typical week]{Typical week}

% \textbf{Topics}: stuff

% \noindent \textbf{Reading}: required vs optional


% \vspace{1cm}
% \noindent \textbf{Suggested problems (do not hand in)}s

% \noindent \textbf{Assignment, due Tuesday, November 23, via Canvas}:

% \noindent \textbf{Reading}:


% \vspace{1cm}
% \noindent \textbf{Suggested problems (do not hand in)}:

% \noindent \textbf{Assignment, due Tuesday, ???, via Canvas}

% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}

% \newpage

 \end{document}

